---
title: Scarlett Winters' Resume
author: Scarlett Winters
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
library(rmarkdown)
library(knitr)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- TRUE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')


# First let's get the data, filtering to only the items tagged as
# Resume items
position_data <- read_csv('positions.csv') %>% 
  filter(in_resume) 
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> winters.scarlett.e@gmail.com
- <i class="fa fa-linkedin"></i> [/scarlett-winters](https://www.linkedin.com/in/scarlett-winters/)
- <i class="fa fa-github"></i> [Portfolio on Github](https://github.com/scarlett425/portfolio)
- <i class="fa fa-phone"></i> (312) 805-9540

Skills {#skills}
--------------------------------------------------------------------------------

- SQL
- R (tidyverse)
- Python (pandas, scikit-learn, numpy)
- Data analysis
- Data collection
- Technical documentation
- Data reporting
- Project management
- Public presentations
- Technical training
- Requirements analysis
- SDLC
- Code review

Fun Facts {#projects}
--------------------------------------------------------------------------------

- This resume was written using the pagedown package in R.

- I am a board member for [R-Ladies Chicago](https://rladieschicago.org), which empowers marginalized genders to be data science leaders.

- My pasttimes include Krav Maga, cooking, and watching documentaries. Ask me what my favorite documentaries are.


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown). 

Source code: [github.com/nstrayer/cv](https://github.com/scarlett425/cv)

Last updated on `r Sys.Date()`.

Main
================================================================================

Scarlett Winters {#title}
--------------------------------------------------------------------------------

Positions {data-icon=suitcase}
--------------------------------------------------------------------------------


```{r}
position_data %>% print_section('professional_experience')
```


Non-9-5 Projects {data-icon=laptop}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('academic_achievements')
```

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```
